Analyzing Coopetition Strategies of Services within Communities

### 2012-11-22 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

In this section, we provide an empirical analysis over the
observed results regarding the characteristics of intelligent web
services hosted in different communities of web services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, web services as service providers, and
master web services as community representatives. These entities
are developed with respect to what is explained in Section
\ref{Preliminaries}. The objective is to investigate the
effectiveness of the proposed strategic system on intelligent
web services' overall budget. %Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
We study the overall performance of the community hosting the
reasoning-empowered web services compared to the ones hosting
stochastic and purely competitive services. The simulation
application is written in \textit{C\#} using \textit{Visual Studio}. Developed web services are initialized with values taken
from a real dataset that includes $2507$ real web services
functioning on the web. The dataset records the QoS values of $9$
parameters including \textit{availability}, \textit{throughput},
and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.

>>>>

In this section, we provide an empirical analysis over the
observed results regarding the characteristics of intelligent web
services hosted in different communities of web services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, web services as service providers, and
master web services as community representatives. These entities
are developed with respect to what is explained in Section
\ref{Preliminaries}. The objective is to investigate the
effectiveness of the proposed strategic system on intelligent
web services' overall budge and also the average QoS of tasks performed by 
community web services which directly affects user satisfaction. 
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
We study the overall performance of the community hosting the
reasoning-empowered web services compared to the ones hosting
stochastic and purely competitive services. The simulation
application is written in \textit{C\#} using \textit{Visual Studio}. 
Developed web services are initialized with values taken
from a real dataset that includes $2507$ real web services
functioning on the web. The dataset records the QoS values of $9$
parameters including \textit{availability}, \textit{throughput},
and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.
